Fixing Vulnerabilities Hinders Maintainability

### 2019-02-03 paper/ICPC19/icpc19.tex
fixed sentence

The impact of each type of security refactoring on the maintainability of
open-source software is presented in Figure~\ref{fig:pat}. The results of the
Wilcoxon signed-rank test by pattern returned statistical evidence which
supports that the maintainability of open-source software decreases for $4$
different patterns: \emph{Broken Autentication} (p = $0.018$),
\emph{Denial-of-Service} (p = $0.029$), \emph{Memory Leak} (p = $0.009$) and
\emph{Miscellaneous} (p = $3.07$x$10^{-4}$). The results also returned
statistical significance that evidence that maintainability is more likely to
not suffer differences for open-source software after removing \emph{Components
with Known Vulnerabilities}\Luis{o resultado e bem diferente dos regular
commits. este refactoring tem alguma particularidade para deixar a
maintainability intacta? convém falar sobre isso na discussão} (p =
$7.96$x$10^{-4}$) and fixing \emph{Cross-Site Scripting Vulnerabilities} (p =
$0.001$). \emph{Injection} and \emph{Cross-Site Request Forgery} produced more
cases where the refactorings had a negative impact in the maintainability.
However, the results obtained for these patterns are not statistically
significant.

@@

This study also exhibits evidence that some patterns need more attention than
others. \emph{Broken Autentication} issues, \emph{Denial-of-Service} attacks and
\emph{Memory Leaks} endure maintainability in $55.3\%$, $51.3\%$, and $47.5\%$,
respectively. Following the implications of our work, we draw attention for the
need of trustful security frameworks, code best practices documentation to
produce safe and maintainable code, proper authorization mechanisms design and
implementation, better tools to introduce in the CI/CD pipeline to help software
maintenance and new or improved programming languages to allow developers to
easily implement safety in their software without endangering maintainability.

>>>>

The impact of each type of security refactoring on the maintainability of
open-source software is presented in Figure~\ref{fig:pat}. The results of the
Wilcoxon signed-rank test by pattern returned statistical evidence which
supports that the maintainability of open-source software decreases for $4$
different patterns: \emph{Broken Autentication} (p = $0.018$),
\emph{Denial-of-Service} (p = $0.029$), \emph{Memory Leak} (p = $0.009$) and
\emph{Miscellaneous} (p = $3.07$x$10^{-4}$). With statistical significance,
results demonstrate evidence that maintainability is not negatively impacted
when removing \emph{Components with Known Vulnerabilities} (p = $7.96$x$10^{-4}$)
and fixing \emph{Cross-Site Scripting Vulnerabilities} (p = $0.001$).
\emph{Injection} and \emph{Cross-Site Request Forgery} produced more
cases where the refactorings had a negative impact in the maintainability.
However, the results obtained for these patterns are not statistically
significant.

@@

This study also exhibits evidence that some security patterns need more attention than
others. \emph{Broken Autentication} issues, \emph{Denial-of-Service} attacks and
\emph{Memory Leaks} endure maintainability in $55.3\%$, $51.3\%$, and $47.5\%$,
respectively. Following the implications of our work, we draw attention for the
need of trustful security frameworks, code best practices documentation to
produce safe and maintainable code, proper authorization mechanisms design and
implementation, better tools to introduce in the CI/CD pipeline to help software
maintenance and new or improved programming languages to allow developers to
easily implement safety in their software without endangering maintainability.
